The Rapid Cycleway Prioritisation Tool

### 2020-06-15 rapid-slides.Rmd
Add existing cycleways slide

@@

- All road sections with spare lanes or estimated width > 10 m (CyIPT)
- Of those, which have a minum continuous length of at least 500 m?
- Rank the roads by cycling potential (commute + school, Government Target)
- Show the top n, where n depends on the size of the region (70 in London)

@@

# How does the tool identify what a ‘cohesive network’ might look like?

>>>>

### Existing cycleways

- Aims to identify **immediate** issues
- From OpenStreetMap, March 2020
- Contains sections of variable quality
- Aim to highligh where gaps need to be filled

![](https://raw.githubusercontent.com/cyipt/popupCycleways/master/figures/results-cycleways-leeds.png)

@@

- Aims to identify **short term priorities**
- All road sections with spare lanes or estimated width > 10 m (CyIPT)
- Of those, which have a minum continuous length of at least 500 m?
- Rank the roads by cycling potential (commute + school, Government Target)
- Show the top n, where n depends on the size of the region (70 in London)

@@

### How to identify a ‘cohesive network’?

- Aims to support **long term planning**
- Intended to show what a joined-up cycle network could look like if we were to consider new cycleways by either closing roads to motorised traffic or creating one-way systems
- Find  roads that have high cycling potential on some or all of their length
- Join them up

![](https://raw.githubusercontent.com/cyipt/popupCycleways/master/figures/results-cohesive-leeds.png)
